Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2016-09-21 paper/letter.tex
more explanation of emcee + some typos

%\url{http://vizier.u-strasbg.fr/cgi-bin/VizieR?-source=B/2mass}
% TOLOLO 00021
%https://ned.ipac.caltech.edu/cgi-bin/objsearch?objname=Tol+21&extend=no&hconst=73&omegam=0.27&omegav=0.73&corr_z=1&out_csys=Equatorial&out_equinox=J2000.0&obj_sort=RA+or+Longitude&of=pre_text&zv_breaker=30000.0&list_limit=5&img_stamp=YES 
\tol receding velocity is $7785\pm 50$km s$^{-1}$, which translates
into a distance of $106.6$ Mpc (with the Hubble constant $H_{0}$=73
Mpc km s$^{-1}$) 
Its metallicity is $\sim Z_{\odot}/24$ \cite{Izotov04} as derived from optical
spectroscopy.

@@

The near-infrared fluxes at $3.6$ $\mu$m and $4.5$ $\mu$m are
$7.71\pm0.55\times 10^{-5}$ Jy and $7.98\pm0.71\times 10^{-5}$ Jy
\cite{2008ApJ...678..804E}.  Using a convertion betwen fluxes and
stellar mass calibrted on the Large Magellanic Cloud $M_{\star} =
10^{5.65} \times F_{3.6}^{2.85} \times F_{4.5}^{-1.85} \times
(D/0.05)^2 M_{\odot}$, where fluxes are in Jy and $D$ is the luminosity
distance to the source in Mpc, we find $M_{\star} = 1.45\pm0.45\times 10^{8}
M_{\odot}$, with a $30\%$ uncertainty coming from the callibration
process \cite{2012AJ....143..139E}.

@@

The analytical solution for the rotation sphere was the base to
perform the Markov Chain Monte Carlo Calculation using the
\texttt{emcee} implementation.
We explore flat priors on $V_{\rm max}$ $\log_{10}\tau$, $\log_{10} T$ and
$\theta$ using $500$ steps with $24$ walkers for a total of $12000$
points.
The results are summarized in Figure \ref{emceeresults}. 
From this model we find that the fiducial parameters that could
explain the broad features in \tol\ are $V_{\rm max}=348^{+75}_{-48}$
km s$^{-1}$, $\log \tau = 6.96^{+0.26}_{-0.18}$, $\log_{10} T/\mathrm
{K} = 4.27^{+0.11}_{-0.18}$ and  $\theta = 35.78^{+2.13}_{-1.88}$ degrees.

\begin{figure}
\begin{center}
\includegraphics[width=1.0\textwidth]{emcee_results.pdf}
\caption{{\bf Results from the Markov Chain Monte Carlo compuation for
    the rotation model.}\label{emceeresults}} 
\end{center}
\end{figure}

\section*{The Outflow Model}
The galaxy outflow model is a highly sucessful framework to fit
and interprete \lya\ line observations.

@@

In the rotation model the size of the spherical region, $r_{s}$, can
be infered from the relationship $\tau = \sigma_0 n r_s$, where
$\sigma_0=5.898\times 10^{-14}$cm$^{-2}$ is the Lyman$\alpha$
cross section at the  line's center, $n$ is the number density. 
This expresion can be rewritten as
\begin{equation}
r_{s} = 0.055 \left(\frac{\tau}{10^7}\right) \left(
\frac{\mathrm{atoms\ cm^{-3}}}{n}\right) \mathrm{kpc}.
\end{equation}
%
Using this result and assuming a bound for the number density of
$0.01<n/\mathrm{atoms\ cm^{-3}}<0.1$ we have $0.55
< r_s/\mathrm{kpc}<5.5$.

This is consistent with the  constraint on the total HI mass and the
optical depth $\tau_0$ as we show next. The total HI mass can be
approximated as $M_H = \frac{4\pi}{3} m_H n r_s^3$, where
$m_H=1.67\times 10^{-24}$ gr is the mass of a single Hydrogen atom.
This allows us to write the total hydrogen mass as
\begin{equation}
M_{H} = 5.70 \times 10^{6} \left(\frac{\tau}{10^{7}}\right)
\left(\frac{r_s}{\mathrm{kpc}}\right)^2 M_{\odot}
\end{equation}
%
The uppper limit from the HI mass non-detection imposes $r_{s} <
6.81$ kpc, which is consistent with the bound we found in the first
place, as we wanted to show.

>>>>

%\url{http://vizier.u-strasbg.fr/cgi-bin/VizieR?-source=B/2mass}
% TOLOLO 00021
%https://ned.ipac.caltech.edu/cgi-bin/objsearch?objname=Tol+21&extend=no&hconst=73&omegam=0.27&omegav=0.73&corr_z=1&out_csys=Equatorial&out_equinox=J2000.0&obj_sort=RA+or+Longitude&of=pre_text&zv_breaker=30000.0&list_limit=5&img_stamp=YES 
\tol\ receding velocity is $7785\pm 50$km s$^{-1}$, which translates
into a distance of $106.6$ Mpc (with the Hubble constant $H_{0}$=73
Mpc km s$^{-1}$) 
Its metallicity is $\sim Z_{\odot}/24$ \cite{Izotov04} as derived from optical
spectroscopy.

@@

The near-infrared fluxes at $3.6$ $\mu$m and $4.5$ $\mu$m are
$7.71\pm0.55\times 10^{-5}$ Jy and $7.98\pm0.71\times 10^{-5}$ Jy
\cite{2008ApJ...678..804E}.  Using a conversion between fluxes and
stellar mass calibrated on the Large Magellanic Cloud $M_{\star} =
10^{5.65} \times F_{3.6}^{2.85} \times F_{4.5}^{-1.85} \times
(D/0.05)^2 M_{\odot}$, where fluxes are in Jy and $D$ is the luminosity
distance to the source in Mpc, we find $M_{\star} = 1.45\pm0.45\times 10^{8}
M_{\odot}$, with a $30\%$ uncertainty coming from the calibration
process \cite{2012AJ....143..139E}.

@@

The analytical solution for the rotation sphere was the base to
perform the Markov Chain Monte Carlo (MCMC) calculation using the
\texttt{emcee} Python library \cite{2013PASP..125..306F}. \texttt{emcee} 
is an open source optimized implementation of the affine-invariant 
ensemble sampler for MCMC. The algorithm creates a number of walkers that,
during a sufficient number of steps, generate parameters' combinations for
a specific model. For each time, the code calculates the likelihood of the
combination to be \textit{ideal} regarding the observational data. It 
iterates then over the parameter space until it finds the set of
parameters that maximizes the logarithm of likelihood (known as $\chi^2$).

MCMC methods are optimal for sampling parameters at a high number of 
dimensions. In this case we explore flat priors on four: $V_{\rm max}$, 
$\log_{10}\tau$, $\log_{10} T$ and $\theta$ using $500$ steps with $24$ 
walkers for a total of $12000$ points. The results are summarized in 
Figure \ref{emceeresults}. From this model we find that the fiducial 
parameters that could explain the broad features in \tol\ are 
$V_{\rm max}=348^{+75}_{-48}$ km s$^{-1}$, $\log \tau = 6.96^{+0.26}_{-0.18}$, 
$\log_{10} T/\mathrm {K} = 4.27^{+0.11}_{-0.18}$ and $\theta = 35.78^{+2.13}_{-1.88}$ 
degrees.

\begin{figure}
\begin{center}
\includegraphics[width=1.0\textwidth]{emcee_results.pdf}
\caption{{\bf Results from the Markov Chain Monte Carlo computation for
    the rotation model.} The dotted vertical lines in the outer histograms 
	represent the percentiles 16\%, 50\% and 84\%. \label{emceeresults}} 
\end{center}
\end{figure}

\section*{The Outflow Model}
The galaxy outflow model is a highly successful framework to fit
and interpret \lya\ line observations.

@@

In the rotation model the size of the spherical region, $r_{s}$, can
be inferred from the relationship $\tau = \sigma_0 n r_s$, where
$\sigma_0=5.898\times 10^{-14}$cm$^{-2}$ is the Lyman$\alpha$
cross section at the  line's center, $n$ is the number density. 
This expression can be rewritten as
\begin{equation}
r_{s} = 0.055 \left(\frac{\tau}{10^7}\right) \left(
\frac{\mathrm{atoms\ cm^{-3}}}{n}\right) \mathrm{kpc}.
\end{equation}
%
Using this result and assuming a bound for the number density of
$0.01<n/\mathrm{atoms\ cm^{-3}}<0.1$ we have $0.55
< r_s/\mathrm{kpc}<5.5$.

This is consistent with the  constraint on the total HI mass and the
optical depth $\tau_0$ as we show next. The total HI mass can be
approximated as $M_H = \frac{4\pi}{3} m_H n r_s^3$, where
$m_H=1.67\times 10^{-24}$ gr is the mass of a single Hydrogen atom.
This allows us to write the total hydrogen mass as
\begin{equation}
M_{H} = 5.70 \times 10^{6} \left(\frac{\tau}{10^{7}}\right)
\left(\frac{r_s}{\mathrm{kpc}}\right)^2 M_{\odot}
\end{equation}
%
The upper limit from the HI mass non-detection imposes $r_{s} <
6.81$ kpc, which is consistent with the bound we found in the first
place, as we wanted to show.
